Analysis: NAME

### 2021-07-21 tsq_data.Rmd
added gcfid data and plotted it

```{r}
root <- "data"
all_data <-
  tibble(
    sample = c("a", "b"),
    file = c("TSQ5934_mAx.xls", "TSQ5934_mAx.xls"),
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```

>>>>

```{r}
root <- "data/gc_fid_data_2020/"
file_list = list.files(path = root)
all_data <-
  tibble(
    sample = file_list,
    file = file_list,
    data = map(file.path(root, file), read_chromeleon_export),
    injection_details = map(data, "injection_details"),
    integration_results = map(data, "integration_results")
  ) %>% select(-data)
```
